Linear analysis of the vertical shear instability in astrophysical disks

### 2015-02-02 linear_adia.tex
revised analysis part

\subsection{Spurious growth of adiabatic perturbations in the local
  model}\label{analytic_adia} 
For adiabatic perturbations ($\gamma>1$, $\beta\to\infty$) we may
simply use the Soilberg-Hoiland critera to assess stability
(\S\ref{solberg}). Nevertheless, we briefly consider this case in the
local framework to demonstrate its limitations. For $\beta\to\infty$
the parameter $\chi = 1/\gamma$ and Eq. \ref{vertiso_gov_nondim} can
be written as

>>>>

\subsection{Spurious growth of adiabatic perturbations in the local
  model with vertical shear}\label{analytic_adia} 
For adiabatic perturbations ($\gamma>1$, $\beta\to\infty$) we may
simply use the Soilberg-Hoiland critera to assess stability
(\S\ref{solberg}). Nevertheless, we briefly consider this case in the
local framework to demonstrate its limitations. For $\beta\to\infty$
the parameter $\chi = 1/\gamma$ and Eq. \ref{vertiso_gov_nondim} can
be written as
